### 2018-07-16 manuscript.tex
Update manuscript.tex

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16}, and the actual numbers might in fact higher \cite{GaluKama15} (more?).  The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

@@

\subsection{Research Questions}\label{research-questions}
There are two main research questions in this study:  attitudes of FGC benefits (see the list of FGC benefits at table xx) in association with attitudes of FGC continuance; and attitudes of FGC benefits in association with intention (planned behavior) of cutting daughters and with attitudes of FGC continuance.  The first question is referred to a FGC future model (FGC attitude model?), and the second a FGC daughter model (FGC intention model?).

\_\_{[}CF: how about the third model xx basic daughter model?  A few sentence of the differences between FGC future model and FGC daughter model{]}

@@

The main constructs to test the three theories of FGC practices(e.g., conventions, modernization, and feminism) are inferred from the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm).  The planned behavior theory proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, we constructed women's fgc attitudes based on the xx questions of FGC benefits in DHS, women's gender attitudes based on xx questions of domestic violence; the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.

>>>>

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (to update), and the actual numbers might in fact higher \cite{GaluKama15} (more?).  The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

@@

\subsection{Research Questions}\label{research-questions}
There are two main research questions in this study:  attitudes of FGC benefits (see the list of FGC benefits at table xx) in association with attitudes of FGC continuance; and attitudes of FGC benefits and of FGC continuance in association with intention (planned behavior) of cutting daughters.  The first question is referred to a FGC future model (FGC attitude model?), and the second a FGC daughter model (FGC intention model?).

\_\_{[}CF: how about the third model xx basic daughter model without counting attitudes of FGC continuance ?  A few sentence of the differences between FGC future model and FGC daughter model{]}

@@

We conceptualized the main constrcuts in testing the three theories of FGC practice aformentioned based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92}. (to confirm and update) The heory of planned behavior proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, we constructed women's fgc attitudes based on the xx questions of FGC benefits in DHS, women's gender attitudes based on xx questions of domestic violence; the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.
